---
title: "R Tidbits"
output:
  github_document:
    toc: true
# output:
#   html_document:
#     highlight: pygments
#     toc: true
#     toc_float: true
#     number_sections: true
---

```{r, echo = F}
htmltools::img(src = knitr::image_uri("~/Desktop/logo.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; height:130px; padding:10px;')
```
               
```{r setup, include=FALSE, eval = T}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 80),
  eval = FALSE,
  warning = F
)
```

# Package Development

## Important Commands

### Package Creation
```{r creation}
usethis::create_package()
usethis::use_readme_rmd()
usethis::use_mit_license("Aris Paschalidis")
usethis::use_spell_check()
usethis::use_namespace()
usethis::use_pipe()
usethis::use_lifecycle_badge("Experimental")
```

### CI and Testing
```{r CI and testing}
usethis::use_travis()
usethis::use_testthat()
usethis::use_github_actions()

## Note can add more specific actions using
usethis::use_github_action("check-standard")
```

## Websites

The following list of sites are particularly handy in package development:

* [R Packages](http://r-pkgs.had.co.nz/)
* [Usethis Reference Page](https://usethis.r-lib.org/reference/index.html)
* [Devtools Reference Page](https://devtools.r-lib.org/reference/index.html)

# Badges

Badges are written in R Markdown with the following structure:

```markdown
[![Badge Name]](url to badge image)(url when click on badge)
```

Some examples:

[![Build Status](https://travis-ci.com/arisp99/CAvaccines.svg?branch=master)](https://travis-ci.com/arisp99/CAvaccines)

<!-- [![R build status](https://github.com/OJWatson/coiaf/workflows/R-CMD-check/badge.svg)](https://github.com/OJWatson/coiaf/actions) -->

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)

[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

The package [`badger`](https://github.com/GuangchuangYu/badger) has a nice list
of badges that can be added.

## Commands
```{r badge commands}
usethis::use_lifecycle_badge()
usethis::use_travis_badge()
usethis::use_github_actions_badge()
```

# Logos

The package [`hexSticker`](https://github.com/GuangchuangYu/hexSticker) is very
neat for making logos. An example is provided below:
```{r example logo}
hexSticker::sticker("~/Desktop/wisdom.jpg", package = "RTidbits", 
                    filename = "~/Desktop/logo.png", 
                    s_x = 0.96, s_y = 0.9, s_width = 1.4,
                    p_size = 6.5, p_x = 1, p_y = 1.6, p_color = "#ed7980",
                    h_color = "#f6ca32", h_fill = "#18478c", 
                    white_around_sticker = T)
```

The website [TinEye](https://labs.tineye.com/color/) may also come in handy for
color matching.

In order to properly format and store the logo in the right place, the following
may come in handy
```{r format logo}
usethis::use_logo("~/Desktop/logo.png")
```

# R Markdown

## Websites

* [R Markdown Book](https://bookdown.org/yihui/rmarkdown/)
* [R Markdown Cheat Sheet](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)
* [Hadley Chapter](https://r4ds.had.co.nz/r-markdown.html#introduction-18)
* [Knitr Options](https://yihui.org/knitr/options/)

# Example Yaml Headers

## HTML
```yaml
---
html_document:
  highlight: pygments
  toc: true
  toc_float: true
  number_sections: true
---
```

## PrettyDoc
```yaml
---
prettydoc::html_pretty:
  theme: hpstr
  highlight: vignette
  toc: true
  number_sections: true
---
```

## PDF
```yaml
---
pdf_document:
  toc: true
  toc_depth: 2
  number_sections: true
---
```


## Multiple Outputs
In order to specifiy multiple outputs, it is as easy as just having both the
html and pdf code above, for example. If however, specific instructions are not
given for one of the outputs, the user must include `output_type: default`.

If multiple outputs are specified, and the user does not specify which, the
first output will be built. In order to build all the outputs at once, the
following must be used

```{r multiple outputs}
rmarkdown::render("path/to/markdown", output_format = "all")
```

# Figures
Figures can be included using the [`knitr`](https://yihui.org/knitr/) package

```{r example image}
knitr::include_graphics("path/to/image")
```

Note that html documents will not accept pdf files; the image must be a png file.

# Misc

In order to ensure that documentation is being built with roxygen2,
Go to Tools -> Project Options -> Build Tools and check the box that says 
"generate documentation with roxygen"

